---
title: "Premier League Dashboard"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
runtime: shiny
---

{r setup, include=FALSE}
library(flexdashboard)

# YELLOW CARD ANALYSIS
Column {data-width=450}
-----------------------------------------------------------------------

### player yellow cards 

```{r}
library(DT)
library(tidyverse)
library(dplyr)
library(rvest)

#DATA FOR PLAYER YELLOWS
url1<-"https://sports.ndtv.com/english-premier-league/stats/most-yellow-cards-player-statsdetail/2020-21"
y=read_html(url1) %>%
html_nodes("table") %>%
html_table() 
ye=data.frame(y)

#ADDITION OF AVG YELLOWS PER GAME 
ye["average"]<-(ye$yellow.card/ye$Games.Played)
yellowcards=head(ye,10)
datatable(yellowcards,options=list(pageLength = 40, lengthMenu = c(2, 12, 18) ))%>%
     formatStyle( 0, target= 'row',color = 'black', lineHeight='100%')

```


### TEAM YELLOW CARDS

```{r}
library(DT)
library(tidyverse)
library(dplyr)
library(rvest)

url2<-"https://sports.ndtv.com/english-premier-league/stats/most-yellow-cards-team-statsdetail/2020-21"
t=read_html(url2) %>%
html_nodes("table") %>%
html_table() 

team=data.frame(t)
teamyellow=head(team,10)
datatable(teamyellow)
```




Column {.tabset .tabset-fade data-width=600}
-----------------------------------------------------------------------

### games played vs yellowcards

```{r}

plot(yellowcards$Games.Played,yellowcards$yellow.card,type="p",xlab ="
     games played", ylab ="yellow cards",main="GAMES PLAYED VS YELLOWCARDS CONCEDED",col=rainbow(10),pch=19)
legend("topleft",legend = yellowcards$Player.Name,col = rainbow(10),cex=0.5,fill = rainbow((10)))

```

### player ranking VS per game yellow card average
```{r}

plot(yellowcards$average,yellowcards$Rank,type="p",xlab ="
     yellow card average per game", ylab ="ranking",main="PLAYER RANKING VS PER GAME YELLOWCARD AVERAGE",col=rainbow(10),pch=19)
legend("bottomleft",legend = yellowcards$Player.Name,col = rainbow(10),cex=0.5,fill = rainbow((10)))
```


### barplot for top 10 players with most yellow
```{r}

barplot(yellowcards$yellow.card, width = 0.4,main ="TOP 10 PLAYERS WITH MOST YELLOW CARDS",col = rainbow(10),xlab="yellow card numbers")
legend("topright",legend = yellowcards$Player.Name,col = rainbow(10),cex=0.4,fill = rainbow((10)))
```

### pieplot for YELLOWS CARDS 20/21(clubs)
```{r}

slices=teamyellow$yellow.card
names=teamyellow$Club.Name
pct=round(slices/sum(slices)*100)
new=paste(pct,"%",sep="")
pie(slices,labels = new,main = "YELLOW CARDS 20/21(clubs)",col=rainbow(10))
legend("topleft",legend=teamyellow$Club.Name,col=rainbow(10),cex = 0.4,fill=rainbow(10))
```


# RED CARD ANALYSIS
Column {data-width=450}
-----------------------------------------------------------------------


### player yellow cards 

{r}
library(DT)
library(tidyverse)
library(dplyr)
library(rvest)

#DATA FOR PLAYER RED

url3<-"https://sports.ndtv.com/english-premier-league/stats/most-red-cards-player-statsdetail/2020-21"
r=read_html(url3) %>%
  html_nodes("table") %>%
  html_table() 
red=data.frame(r)

redcards=head(red,10)
redcards["average"]=(redcards$red.card/redcards$Games.Played)
datatable(redcards)


### TEAM RED CARDS

{r}
library(DT)
library(tidyverse)
library(dplyr)
library(rvest)

url4<-"https://sports.ndtv.com/english-premier-league/stats/most-red-cards-team-statsdetail/2020-21"
tr=read_html(url4) %>%
  html_nodes("table") %>%
  html_table() 
teamred=data.frame(tr)
teamredcards=head(teamred,10)
datatable(teamredcards)




Column {.tabset .tabset-fade data-width=600}
-----------------------------------------------------------------------

### games played vs RED cards

{r}

plot(redcards$Games.Played,redcards$red.card,type="p",xlab ="
     games played", ylab ="red cards",main="GAMES PLAYED VS RED CARDS CONCEDED",col=rainbow(10),pch=19)
legend("topleft",legend = redcards$Player.Name,col = rainbow(10),cex=0.8,fill = rainbow((10)))



### player ranking per game red card average
{R}
plot(redcards$average,redcards$Rank,type="p",xlab ="
     red card average per game", ylab ="ranking",main="PLAYER RANKING VS PER GAME REDCARD AVERAGE",col=rainbow(10),pch=19)
legend("center",legend = redcards$Player.Name,col = rainbow(10),cex=0.5,fill = rainbow((10)))


### correlation between games played vs per game red card average
{r}

#CORRELATION
# Data generation
set.seed(1)
x <- redcards$average
y <- redcards$Games.Played

# Creating the plot
plot(x, y,xlab = "Passes",ylab = "Wins",main = "RELATIONSHIP BETWEEN PER GAME RED CARD AVERAGE AND GAMES PLAYED", pch = 19, col = rainbow(10))

# Regression line
abline(lm(y ~ x), col = "red", lwd = 3)

# Pearson correlation
text(paste("Correlation:", round(cor(x, y), 2)), x = 17000, y = 25)
cd=cor(x,y)




### pie plot
{r}
slices=teamredcards$red.card
names=teamredcards$Club.Name
pct=round(slices/sum(slices)*100)
new=paste(names,"-",pct,"%",sep="")
pie(slices,labels = new,main = "RED CARDS 20/21(club)",col=rainbow(11:20))