---
title: "Premier League Dashboard"
output: 
  flexdashboard::flex_dashboard:
    orientation: column
runtime: shiny
---
```{r setup, include=FALSE}
library(flexdashboard)
```

    Goals
================================
Column {data-width=400}
-----------------------------------------------------------------------
### Number of goals by Player
```{r}
library(tidyverse)
g<-read.csv("C:\\Users\\aayus\\Documents\\premierleaguegoals.csv")
library(DT)
datatable(g,options = list(lengthChange = FALSE,searching=FALSE,paging=FALSE,info=FALSE))
```
### Number of goals by Club
```{r}
library(tidyverse)
w<-read.csv("C:\\Users\\aayus\\Documents\\clubgoals.csv")
library(DT)
datatable(w,options = list(lengthChange = FALSE,searching=FALSE,paging=FALSE,info=FALSE))
```

Column {.tabset .tabset-fade data-width=600}
-----------------------------------------------------------------------

### Goals Conceded

```{r}

#goalsconceded
df<-read.csv("C:\\Users\\aayus\\Documents\\pl_20-21.csv")
library(dplyr)
defenders<-subset(df,Position=="Defender")
defenders<-defenders%>%
  arrange(desc(Appearances)) 
defenders<- head(defenders,10)
defenders["cpg"]<-defenders$Goals.Conceded/defenders$Appearances
library(RColorBrewer)
coul <- brewer.pal(length(defenders$Name), "Paired") 
par(mar=c(5,8,2,3),xpd=TRUE)
plot(defenders$Clean.sheets,defenders$cpg,ylab='Goals conceded per game',cex=defenders$Tackles/70, main ='Goals conceded per game vs Clean sheets',xlab="Clean Sheets",col=coul,pch=20)
legend("bottomleft",defenders$Name, cex = 0.4, fill =coul,inset=c(-0.40,0))
```

### Number of Goals by club
```{r}
cg=read.csv("C:\\Users\\aayus\\Documents\\clubgoals.csv")
ppercent<- paste(round(100*cg$Stat/sum(cg$Stat), 1),"%")
library(RColorBrewer)
coul <- brewer.pal(length(cg$Club), "Paired") 
par(mar=c(5,8,2,3),xpd=TRUE)
pie(cg$Stat,labels=ppercent,main="Goals by Club",col=coul,clockwise = TRUE,radius=1)
legend("bottomleft",cg$Club, cex = 0.6, fill =coul,inset=c(-0.35,0))
```

### Number of goals by player  
```{r}
goals<-read.csv("C:\\Users\\aayus\\Documents\\premierleaguegoals.csv")
par(mar=c(8,5,3,1),xpd=TRUE)
barplot(goals$Stat,main="Goals in Premier league 2020/21",names.arg=goals$Player,las=2,col="#32a87d",ylab = "Number of goals",cex.names = 0.75,ylim=c(0,25))
```

    Shots
================================
Column {data-width=400}
-----------------------------------------------------------------------
### Number of Shots by Player
```{r}
library(tidyverse)
g<-read.csv("C:\\Users\\aayus\\Documents\\premierleagueshots.csv")
library(DT)
datatable(g,options = list(lengthChange = FALSE,searching=FALSE,paging=FALSE,info=FALSE))
```
### Number of Shots by Club
```{r}
library(tidyverse)
w<-read.csv("C:\\Users\\aayus\\Documents\\clubshots.csv")
library(DT)
datatable(w,options = list(lengthChange = FALSE,searching=FALSE,paging=FALSE,info=FALSE))
```

Column {.tabset .tabset-fade data-width=600}
-----------------------------------------------------------------------

### Goals correlation to Shots

```{r}
wt<-read.csv("C:\\Users\\aayus\\Documents\\ShotsGoals.csv")
paste("Correlation:",round(cor(wt$Goals, as.integer(gsub(",","",wt$Shots))), 2))
# Creating the plot
plot(as.integer(gsub(",","",wt$Shots)),wt$Goals ,ylab = "Goals",xlab = "Shots",main = "Relation between number of Shots and Goals", pch = 20, col = "darkblue")
# Regression line
abline(lm (wt$Goals~as.integer(gsub(",","",wt$Shots))), col = "maroon", lwd = 3)

```

### Number of Shots by club
```{r}
cs<-read.csv("C:\\Users\\aayus\\Documents\\clubshots.csv")
ppercent<- paste(round(100*cs$Stat/sum(cs$Stat), 1),"%")
library(RColorBrewer)
coul <- brewer.pal(length(cs$Stat), "Set3") 
par(mar=c(5,8,2,3),xpd=TRUE)
pie(cs$Stat,labels=ppercent,main="Shots by Club",col=coul,clockwise = TRUE,radius=1)
legend("bottomleft",cs$Club, cex = 0.6, fill =coul,inset = c(- 0.42, 0))
```

### Number of Shots by player  
```{r}
shots<-read.csv("C:\\Users\\aayus\\Documents\\premierleagueshots.csv")
par(mar=c(8,5,3,1),xpd=TRUE)
barplot(shots$Stat,main="Shots in Premier league 2020/21",names.arg=shots$Player,las=2,col="#32a87d",ylab = "Number of shots",cex.names = 0.75)
```

    Touches and Player Statistics
================================

Column {data-width=400}
-----------------------------------------------------------------------

### Number of Touches by Player
```{r}
library(tidyverse)
g<-read.csv("C:\\Users\\aayus\\Documents\\premierleaguetouches.csv")
library(DT)
datatable(g,options = list(lengthChange = FALSE,searching=FALSE,paging=FALSE,info=FALSE))
```
### Number of Touches by Club
```{r}
library(tidyverse)
w<-read.csv("C:\\Users\\aayus\\Documents\\clubtouches.csv")
library(DT)
datatable(w,options = list(lengthChange = FALSE,searching=FALSE,paging=FALSE,info=FALSE))
```

Column {.tabset .tabset-fade data-width=600}
-----------------------------------------------------------------------
### Player Statistics

```{r}
#radar chart
df2<-read.csv("C:\\Users\\aayus\\Downloads\\football.csv")
library(fmsb)
pl<-subset(df2,Player.Name=="Harry Kane")
pl3<-subset(df2,Player.Name=="Bruno Fernandes")
pl2<-subset(df2,Player.Name=="Mohamed Salah")
pls<-data.frame(pl['Goals.Per.Match'],pl['Passes.Per.Match'],pl['Shooting.Accuracy..'],pl['Appearances'],pl['Shots.On.Target'])
pls2<-data.frame(pl2['Goals.Per.Match'],pl2['Passes.Per.Match'],pl2['Shooting.Accuracy..'],pl2['Appearances'],pl2['Shots.On.Target'])
pls3<-data.frame(pl3['Goals.Per.Match'],pl3['Passes.Per.Match'],pl3['Shooting.Accuracy..'],pl3['Appearances'],pl3['Shots.On.Target'])
max_min <- data.frame(Goals.Per.Match = c(1,0),Passes.Per.Match=c(100,0),Shooting.Accuracy..=c(50,0),Appearances=c(1000,0),Shots.On.Target=c(500,0))
rownames(max_min) <- c("Max", "Min")
# Bind the variable ranges to the data
dfn<-rbind(max_min,pls,pls2,pls3)
pldata<-dfn[c("Max", "Min", "498","7","155"), ]
colors_border=c(rgb(0.7,0.5,0.1,0.4), rgb(0.2,0.5,0.5,0.4), rgb(0.8,0.2,0.5,0.4) )
colors_in=c(rgb(0.7,0.5,0.1,0.4), rgb(0.2,0.5,0.5,0.4), rgb(0.8,0.2,0.5,0.4) )
radarchart(pldata,title="Player Stats for Top 3 Goal Scorers",cglcol="grey", cglty=1, axislabcol="grey",pcol=colors_border,pfcol = colors_in);
legend("topleft",legend = c("Harry Kane","Mohamed Salah","Bruno Fernandes"), bty = "n", pch=20 , col=colors_in , text.col = "black", cex=0.8, pt.cex=3)

```

### Number of touches by player
```{r}
touches<-read.csv("C:\\Users\\aayus\\Documents\\premierleaguetouches.csv")
par(mar=c(8,5,3,1),xpd=TRUE)
barplot(as.integer(gsub(",","",touches$Stat)),main="Touches in Premier league 2020/21",names.arg=touches$Player,las=2,col="#32a87d",ylab = "Number of touches",cex.names = 0.75)

```

### Number of touches by club

```{r}
touchesclub<-read.csv("C:\\Users\\aayus\\Documents\\clubtouches.csv")
ppercent<- paste(round(100*as.integer(gsub(",","",touchesclub$Stat))/sum(as.integer(gsub(",","",touchesclub$Stat))), 1),"%")
library(RColorBrewer)
coul <- brewer.pal(length(touchesclub$Stat), "Set3") 
par(mar=c(5,8,2,3),xpd=TRUE)
pie(as.integer(gsub(",","",touchesclub$Stat)),labels=ppercent,main="Touches by Club",col=coul,clockwise = TRUE,radius=1)
legend("bottomleft",touchesclub$Club, cex = 0.6, fill =coul,inset = c(- 0.40, 0))
```
    
    Correlation with Wins
================================
Column {.tabset .tabset-fade data-width=1000}
-----------------------------------------------------------------------
### Shots

```{r}

#correlation of wins and Shots

wt<-read.csv("C:\\Users\\aayus\\Documents\\WinsShots.csv")
paste("Correlation:", round(cor(wt$Wins, as.integer(gsub(",","",wt$Shots))), 2))

# Creating the plot
plot(as.integer(gsub(",","",wt$Shots)),wt$Wins ,ylab = "Wins",xlab = "Shots",main = "Relation between number of Shots and Wins", pch = 20, col = "darkblue")

# Regression line
abline(lm (wt$Wins~as.integer(gsub(",","",wt$Shots))), col = "maroon", lwd = 3)

```

### Touches

```{r}
#correlation of wins and touches

wt<-read.csv("C:\\Users\\aayus\\Documents\\Winstouches.csv")
paste("Correlation:", round(cor(wt$Wins, as.integer(gsub(",","",wt$Touches))), 2))
# Creating the plot
plot(as.integer(gsub(",","",wt$Touches)),wt$Wins ,ylab = "Wins",xlab = "Touches",main = "Relation between number of Touches and Wins", pch = 20, col = "darkblue")

# Regression line
abline(lm (wt$Wins~as.integer(gsub(",","",wt$Touches))), col = "maroon", lwd = 3)

# Pearson correlation
```

### Tackles
```{r}
wt<-read.csv("C:\\Users\\aayus\\Documents\\WinsTackles.csv")
paste("Correlation:", round(cor(wt$Wins, as.integer(gsub(",","",wt$Tackles))), 2))
# Creating the plot
plot(wt$Tackles,as.integer(gsub(",","",wt$Wins)) ,xlab = "Tackles",ylab = "Wins",main = "Relation between number of Tackles and Wins", pch = 20, col = "darkblue")
# Regression line
abline(lm(wt$Wins~as.integer(gsub(",","",wt$Tackles))), col = "maroon", lwd = 3)
# Pearson correlation
```
