---
title: "ZERO1"
output: 
  flexdashboard::flex_dashboard:
    orientation: column
runtime: shiny
---
<style>
.navbar {
  margin: 0;
  padding: 0;
  height: 100%;
  display: block;
  position: fixed;
  width: 150px; 
  background:black;
  font-weight:700;
}

body {
          margin-left: 200px; 
          padding-top:0px
}
</style>


```{r setup, include=FALSE}
library(flexdashboard)

```
    Goals
================================
Column {data-width=400}
-----------------------------------------------------------------------
### Number of goals by Player
```{r}
library(tidyverse)
g<-read.csv("C:/Users/athar/Desktop/ZER01/Aayush code/premierleaguegoals.csv")
library(DT)
datatable(g,options = list(lengthChange = FALSE,searching=FALSE,paging=FALSE,info=FALSE))
```
### Number of goals by Club
```{r}
library(tidyverse)
#w<-read.csv("C:\\Users\\aayus\\Documents\\clubgoals.csv")
w<-read.csv("C:/Users/athar/Desktop/ZER01/Aayush code/clubgoals.csv")
library(DT)
datatable(w,options = list(lengthChange = FALSE,searching=FALSE,paging=FALSE,info=FALSE))
```

Column {.tabset .tabset-fade data-width=600}
-----------------------------------------------------------------------

### Goals Conceded

```{r}

#goalsconceded
df<-read.csv("C:/Users/athar/Desktop/ZER01/Aayush code/pl_20-21.csv")
library(dplyr)
defenders<-subset(df,Position=="Defender")
defenders<-defenders%>%
  arrange(desc(Appearances)) 
defenders<- head(defenders,10)
defenders["cpg"]<-defenders$Goals.Conceded/defenders$Appearances
library(RColorBrewer)
coul <- brewer.pal(length(defenders$Name), "Paired") 
par(mar=c(5,8,2,3),xpd=TRUE)
plot(defenders$Clean.sheets,defenders$cpg,ylab='Goals conceded per game',cex=defenders$Tackles/70, main ='Goals conceded per game vs Clean sheets',xlab="Clean Sheets",col=coul,pch=20)
legend("bottomleft",defenders$Name, cex = 0.4, fill =coul,inset=c(-0.40,0))
```

### Number of Goals by club
```{r}
cg=read.csv("C:/Users/athar/Desktop/ZER01/Aayush code/clubgoals.csv")
ppercent<- paste(round(100*cg$Stat/sum(cg$Stat), 1),"%")
library(RColorBrewer)
coul <- brewer.pal(length(cg$Club), "Paired") 
par(mar=c(5,8,2,3),xpd=TRUE)
pie(cg$Stat,labels=ppercent,main="Goals by Club",col=coul,clockwise = TRUE,radius=1)
legend("bottomleft",cg$Club, cex = 0.6, fill =coul,inset=c(-0.35,0))
```

### Number of goals by player  
```{r}
goals<-read.csv("C:/Users/athar/Desktop/ZER01/Aayush code/premierleaguegoals.csv")
par(mar=c(8,5,3,1),xpd=TRUE)
barplot(goals$Stat,main="Goals in Premier league 2020/21",names.arg=goals$Player,las=2,col="#32a87d",ylab = "Number of goals",cex.names = 0.75,ylim=c(0,25))
```

### Correlation
```{r}
wt<-read.csv("C:/Users/athar/Desktop/ZER01/Aayush code/WinsTackles.csv")
paste("Correlation:", round(cor(wt$Wins, as.integer(gsub(",","",wt$Tackles))), 2))
# Creating the plot
plot(wt$Tackles,as.integer(gsub(",","",wt$Wins)) ,xlab = "Tackles",ylab = "Wins",main = "Relation between number of Tackles and Wins", pch = 20, col = "darkblue")
# Regression line
abline(lm(wt$Wins~as.integer(gsub(",","",wt$Tackles))), col = "maroon", lwd = 3)
# Pearson correlation
```

    Shots
================================
Column {data-width=400}
-----------------------------------------------------------------------
### Number of Shots by Player
```{r}
library(tidyverse)
g<-read.csv("C:/Users/athar/Desktop/ZER01/Aayush code/premierleagueshots.csv")
library(DT)
datatable(g,options = list(lengthChange = FALSE,searching=FALSE,paging=FALSE,info=FALSE))
```
### Number of Shots by Club
```{r}
library(tidyverse)
w<-read.csv("C:/Users/athar/Desktop/ZER01/Aayush code/clubshots.csv")
library(DT)
datatable(w,options = list(lengthChange = FALSE,searching=FALSE,paging=FALSE,info=FALSE))
```

Column {.tabset .tabset-fade data-width=600}
-----------------------------------------------------------------------

### Goals correlation to Shots

```{r}
wt<-read.csv("C:/Users/athar/Desktop/ZER01/Aayush code/ShotsGoals.csv")
paste("Correlation:",round(cor(wt$Goals, as.integer(gsub(",","",wt$Shots))), 2))
# Creating the plot
plot(as.integer(gsub(",","",wt$Shots)),wt$Goals ,ylab = "Goals",xlab = "Shots",main = "Relation between number of Shots and Goals", pch = 20, col = "darkblue")
# Regression line
abline(lm (wt$Goals~as.integer(gsub(",","",wt$Shots))), col = "maroon", lwd = 3)

```

### Number of Shots by club
```{r}
cs<-read.csv("C:/Users/athar/Desktop/ZER01/Aayush code/clubshots.csv")
ppercent<- paste(round(100*cs$Stat/sum(cs$Stat), 1),"%")
library(RColorBrewer)
coul <- brewer.pal(length(cs$Stat), "Set3") 
par(mar=c(5,8,2,3),xpd=TRUE)
pie(cs$Stat,labels=ppercent,main="Shots by Club",col=coul,clockwise = TRUE,radius=1)
legend("bottomleft",cs$Club, cex = 0.6, fill =coul,inset = c(- 0.42, 0))
```

### Number of Shots by player  
```{r}
shots<-read.csv("C:/Users/athar/Desktop/ZER01/Aayush code/premierleagueshots.csv")
par(mar=c(8,5,3,1),xpd=TRUE)
barplot(shots$Stat,main="Shots in Premier league 2020/21",names.arg=shots$Player,las=2,col="#32a87d",ylab = "Number of shots",cex.names = 0.75)
```

### Correlation

```{r}

#correlation of wins and Shots

wt<-read.csv("C:/Users/athar/Desktop/ZER01/Aayush code/WinsShots.csv")
paste("Correlation:", round(cor(wt$Wins, as.integer(gsub(",","",wt$Shots))), 2))

# Creating the plot
plot(as.integer(gsub(",","",wt$Shots)),wt$Wins ,ylab = "Wins",xlab = "Shots",main = "Relation between number of Shots and Wins", pch = 20, col = "darkblue")

# Regression line
abline(lm (wt$Wins~as.integer(gsub(",","",wt$Shots))), col = "maroon", lwd = 3)

```

    Touches
================================

Column {data-width=400}
-----------------------------------------------------------------------

### Number of Touches by Player
```{r}
library(tidyverse)
g<-read.csv("C:/Users/athar/Desktop/ZER01/Aayush code/premierleaguetouches.csv")
library(DT)
datatable(g,options = list(lengthChange = FALSE,searching=FALSE,paging=FALSE,info=FALSE))
```
### Number of Touches by Club
```{r}
library(tidyverse)
w<-read.csv("C:/Users/athar/Desktop/ZER01/Aayush code/clubtouches.csv")
library(DT)
datatable(w,options = list(lengthChange = FALSE,searching=FALSE,paging=FALSE,info=FALSE))
```

Column {.tabset .tabset-fade data-width=600}
-----------------------------------------------------------------------
### Player Statistics

```{r}
#radar chart
df2<-read.csv("C:/Users/athar/Desktop/ZER01/Aayush code/football.csv")
library(fmsb)
pl<-subset(df2,Player.Name=="Harry Kane")
pl3<-subset(df2,Player.Name=="Bruno Fernandes")
pl2<-subset(df2,Player.Name=="Mohamed Salah")
pls<-data.frame(pl['Goals.Per.Match'],pl['Passes.Per.Match'],pl['Shooting.Accuracy..'],pl['Appearances'],pl['Shots.On.Target'])
pls2<-data.frame(pl2['Goals.Per.Match'],pl2['Passes.Per.Match'],pl2['Shooting.Accuracy..'],pl2['Appearances'],pl2['Shots.On.Target'])
pls3<-data.frame(pl3['Goals.Per.Match'],pl3['Passes.Per.Match'],pl3['Shooting.Accuracy..'],pl3['Appearances'],pl3['Shots.On.Target'])
max_min <- data.frame(Goals.Per.Match = c(1,0),Passes.Per.Match=c(100,0),Shooting.Accuracy..=c(50,0),Appearances=c(1000,0),Shots.On.Target=c(500,0))
rownames(max_min) <- c("Max", "Min")
# Bind the variable ranges to the data
dfn<-rbind(max_min,pls,pls2,pls3)
pldata<-dfn[c("Max", "Min", "498","7","155"), ]
colors_border=c(rgb(0.7,0.5,0.1,0.4), rgb(0.2,0.5,0.5,0.4), rgb(0.8,0.2,0.5,0.4) )
colors_in=c(rgb(0.7,0.5,0.1,0.4), rgb(0.2,0.5,0.5,0.4), rgb(0.8,0.2,0.5,0.4) )
radarchart(pldata,title="Player Stats for Top 3 Goal Scorers",cglcol="grey", cglty=1, axislabcol="grey",pcol=colors_border,pfcol = colors_in);
legend("topleft",legend = c("Harry Kane","Mohamed Salah","Bruno Fernandes"), bty = "n", pch=20 , col=colors_in , text.col = "black", cex=0.8, pt.cex=3)

```

### Number of touches by player
```{r}
touches<-read.csv("C:/Users/athar/Desktop/ZER01/Aayush code/premierleaguetouches.csv")
par(mar=c(8,5,3,1),xpd=TRUE)
barplot(as.integer(gsub(",","",touches$Stat)),main="Touches in Premier league 2020/21",names.arg=touches$Player,las=2,col="#32a87d",ylab = "Number of touches",cex.names = 0.75)

```

### Number of touches by club

```{r}
touchesclub<-read.csv("C:/Users/athar/Desktop/ZER01/Aayush code/clubtouches.csv")
ppercent<- paste(round(100*as.integer(gsub(",","",touchesclub$Stat))/sum(as.integer(gsub(",","",touchesclub$Stat))), 1),"%")
library(RColorBrewer)
coul <- brewer.pal(length(touchesclub$Stat), "Set3") 
par(mar=c(5,8,2,3),xpd=TRUE)
pie(as.integer(gsub(",","",touchesclub$Stat)),labels=ppercent,main="Touches by Club",col=coul,clockwise = TRUE,radius=1)
legend("bottomleft",touchesclub$Club, cex = 0.6, fill =coul,inset = c(- 0.40, 0))
```
### Correlation

```{r}
#correlation of wins and touches

wt<-read.csv("C:/Users/athar/Desktop/ZER01/Aayush code/Winstouches.csv")
paste("Correlation:", round(cor(wt$Wins, as.integer(gsub(",","",wt$Touches))), 2))
# Creating the plot
plot(as.integer(gsub(",","",wt$Touches)),wt$Wins ,ylab = "Wins",xlab = "Touches",main = "Relation between number of Touches and Wins", pch = 20, col = "darkblue")

# Regression line
abline(lm (wt$Wins~as.integer(gsub(",","",wt$Touches))), col = "maroon", lwd = 3)

# Pearson correlation
```
    
# Passes

Column {data-width=400}
-----------------------------------------------------------------------

### Data for individual player

```{r}

passes <-read.csv("passes1.csv")
library(DT)
datatable(passes)
```
### Data for top 10 teams

```{r}

w <-read.csv("passes_wins.csv")
library(DT)

# datatable(passes, options=list(
      # pageLength = 20,
      # lengthMenu = c(2, 12, 18)
       #))%>%
     # formatStyle( 0, target= 'row',color = 'black', fontWeight ='bold', lineHeight='100%')

datatable(w)
```

Column {.tabset .tabset-fade data-width=600}
-----------------------------------------------------------------------

### Bar graph

```{r}

#passes <-read.csv("passes1.csv")

#midpts<-barplot(passes$Stat,ylab="Total passes",col=rgb(0.8,0.1,0.1,0.6),main="Stats for passes",cex.names = 0.8,las = 2,ylim = c(0, 1000))

#grid(nx = NA, ny = NULL, lwd = 1, lty = 1, col = "gray")

#text(passes$Player,
     #x = midpts,
     #offset = -0.1,
     #y = -20,
     #cex = 0.8,
     #srt = 40,
     #xpd = TRUE,
     #pos = 2 )

library(plotly)

fig <- plot_ly(
  x = c(passes$Player),
  y = c(passes$Stat),
  name = "SF Zoo",
  type = "bar"
  
)

fig <- fig %>% layout(title = "Stats for passes of top 10 players",
         xaxis = list(title = ""),
         yaxis = list(title = "Passes"))

fig

```

### Pie chart

```{r}
#passes <-read.csv("passes1.csv")
#w <-read.csv("passes_wins.csv")
#piepercent<- round(100*w$Passes/sum(w$Passes), 1)


#legend("topright", legend =w$Passes, cex = 0.6,fill = rainbow(10))



#piepercent<- round(100*w$Passes/sum(w$Passes), 1)
#pie(w$Fouls, labels = piepercent, main = "Total fouls by each club in percentage",col = rainbow(10))
#pie(w$Passes,labels =piepercent,col=rainbow(10),main="Total passes by each club")
#legend("topright", legend =w$Club, cex = 0.6,fill = rainbow(10))
library(plotly)
w <-read.csv("passes_wins.csv")

w<- data.frame("Clubs"=rownames(w), w)

data <- w[,c('Club', 'Passes')]

fig <- plot_ly(data, labels = ~Club, values = ~Passes, type = 'pie')

fig <- fig %>% layout(title = 'Stats for passes of top 10 teams',
         xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
         yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE))

fig

```

### Correlation

```{r}
w <-read.csv("passes_wins.csv")

# Data generation
set.seed(1)
x <- w$Passes
y <- w$Wins

# Creating the plot
plot(x, y,xlab = "Passes",ylab = "Wins",main = "Relation between number of Passes and Wins", pch = 19, col = "blue")

# Regression line
abline(lm(y ~ x), col = "red", lwd = 3)

# Pearson correlation
text(paste("Correlation:", round(cor(x, y), 2)), x = 17000, y = 25)

```

# Assists
Column {data-width=400}
-----------------------------------------------------------------------

### Data for individual player

```{r}

assists <-read.csv("assists1.csv")
library(DT)


datatable(assists)

```
### Data for top 10 teams

```{r}
w <-read.csv("assists_wins.csv")
library(DT)

datatable(w)

```

Column {.tabset .tabset-fade data-width=600}
-----------------------------------------------------------------------

### Bar graph

```{r}

#assists <-read.csv("assists1.csv")


#midpts<-barplot(assists$Stat,ylab="Total assists",col=rgb(0.8,0.1,0.1,0.6),main="Stats for Assists",cex.names = 0.8,las = 2,ylim = c(0, 20))

#grid(nx = NA, ny = NULL, lwd = 1, lty = 1, col = "gray")

#text(assists$Player,
 #    x = midpts,
  #   offset = -0.1,
   #  y = -1,
    # cex = 0.8,
     #srt = 40,
     #xpd = TRUE,
     #pos = 2 )


library(plotly)
assists <-read.csv("assists1.csv")
fig <- plot_ly(
  x = c(assists$Player),
  y = c(assists$Stat),
  name = "SF Zoo",
  type = "bar"
  
)

fig <- fig %>% layout(title = "Stats for assits of top 10 players",
         xaxis = list(title = ""),
         yaxis = list(title = "Assists"))

fig

```

### Scatter Plot

```{r}
#w <-read.csv("assists_wins.csv")
#plot(w$Assists,
 #    w$Goals,
  #   main="Comparing Goals and Assists",
   #  xlab="Assists",
    # ylab="Goals",
     #pch=19,
     #cex=w$Wins/9,
     #cex.axis=1.5,
     #col=rainbow(10))
#legend("bottomright", legend =w$Club, cex = 0.6,fill = rainbow(10))

library(plotly)
w <-read.csv("assists_wins.csv")
d <- w[sample(nrow(w), 10), ]


fig <- plot_ly(
        d, x = ~Assists, y = ~Goals,
        # Hover text:
        text = ~paste("Team: ", Club, '<br>Assists:', Assists,'<br>Wins:', Wins),
        color = ~Assists, size = ~Wins
)
fig <- fig %>% layout(title = "Goals Vs Assists")

fig

```

### Correlation

```{r}
w <-read.csv("assists_wins.csv")

# Data generation
set.seed(1)
x <- w$Assists
y <- w$Wins

# Creating the plot
plot(x, y,xlab = "Assists",ylab = "Wins",main = "Relation between number of Assists and Wins", pch = 19, col = "blue")

# Regression line
abline(lm(y ~ x), col = "red", lwd = 3)

# Pearson correlation
text(paste("Correlation:", round(cor(x, y), 2)), x = 60, y = 25)

```

# Fouls

Column {data-width=400}
-----------------------------------------------------------------------

### Data for individual player

```{r}

fouls <-read.csv("fouls1.csv")
library(DT)


datatable(fouls)

```
### Data for top 10 teams

```{r}
w <-read.csv("fouls_cards.csv")
library(DT)

datatable(w)
```

Column {.tabset .tabset-fade data-width=600}
-----------------------------------------------------------------------

### Bar graph

```{r}

#fouls <-read.csv("fouls1.csv")


#midpts<-barplot(fouls$Stat,ylab="Total fouls",col=rgb(0.8,0.1,0.1,0.6),main="Stats for fouls",cex.names = 0.8,las = 2,ylim = c(0, 100))

#grid(nx = NA, ny = NULL, lwd = 1, lty = 1, col = "gray")

#text(fouls$Player,
 #    x = midpts,
  #   offset = -0.1,
   #  y = -1,
    # cex = 0.8,
     #srt = 40,
     #xpd = TRUE,
     #pos = 2 )

library(plotly)
fouls <-read.csv("fouls1.csv")
fig <- plot_ly(
  x = c(fouls$Player),
  y = c(fouls$Stat),
  name = "SF Zoo",
  type = "bar"
  
)

fig <- fig %>% layout(title = "Stats for fouls of top 10 players",
         xaxis = list(title = ""),
         yaxis = list(title = "Fouls"))

fig

```

### Stacked Bar chart

```{r}
#w <-read.csv("fouls_cards.csv")
#colors = c("red","yellow")
#cards <- c("Red","Yellow")
#Values <- matrix(c(2,1,3,1,5,7,6,1,3,8,5,3,1,2,8,7,4,8,7,9), nrow = 2, ncol = 10, byrow = TRUE)
#barplot(Values, main = "Distribution of red and yellow cards", ylab = "Cards", col = colors,ylim = c(0,20))
#grid(nx = NA, ny = NULL, lwd = 1, lty = 1, col = "gray")
#text(w$Club,
    # x = midpts,
     #offset = -0.1,
     #y = -1,
     #cex = 0.8,
     #srt = 40,
     #xpd = TRUE,
     #pos = 2 )

#legend("topleft", cards, cex = 1, fill = colors)


library(plotly)

x <- c(w$Club)
y1 <- c(w$Red.Cards)
y2 <- c(w$Yellow.Cards)
data <- data.frame(x, y1, y2)

#The default order will be alphabetized unless specified as below:
data$x <- factor(data$x, levels = data[["x"]])

fig <- plot_ly(data, x = ~x, y = ~y1, type = 'bar', name = 'Red Cards', marker = list(color = 'red'))
fig <- fig %>% add_trace(y = ~y2, name = 'Yellow Cards', marker = list(color = 'yellow'))
fig <- fig %>% layout(xaxis = list(title = "Comparing red and yellow cards of top 10 teams", tickangle = -45),
         yaxis = list(title = "Number of cards"),
         margin = list(b = 100),
         barmode = 'group')

fig

```

### Pie Chart

```{r}
#fouls <-read.csv("fouls1.csv")
#w <-read.csv("fouls_cards.csv")
#piepercent<- round(100*w$Fouls/sum(w$Fouls), 1)
#pie(w$Fouls, labels = piepercent, main = "Total fouls by each club in percentage",col = rainbow(10))

#legend("topright", legend =w$Club, cex = 0.6,fill = rainbow(10))

library(plotly)


w<- data.frame("Clubs"=rownames(w), w)

data <- w[,c('Club', 'Fouls')]

fig <- plot_ly(data, labels = ~Club, values = ~Fouls, type = 'pie')

fig <- fig %>% layout(title = 'Stats for fouls',
         xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
         yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE))

fig

```

# Yellow Cards
Column {data-width=450}
-----------------------------------------------------------------------

### player yellow cards 

```{r}
library(DT)
library(tidyverse)
library(dplyr)
library(rvest)

#DATA FOR PLAYER YELLOWS
url1<-"https://sports.ndtv.com/english-premier-league/stats/most-yellow-cards-player-statsdetail/2020-21"
y=read_html(url1) %>%
html_nodes("table") %>%
html_table() 
ye=data.frame(y)

#ADDITION OF AVG YELLOWS PER GAME 
ye["average"]<-(ye$yellow.card/ye$Games.Played)
yellowcards=head(ye,10)
datatable(yellowcards,options=list(pageLength = 40, lengthMenu = c(2, 12, 18) ))%>%
     formatStyle( 0, target= 'row',color = 'black', lineHeight='100%')
```

### TEAM YELLOW CARDS

```{r}
library(DT)
library(tidyverse)
library(dplyr)
library(rvest)

url2<-"https://sports.ndtv.com/english-premier-league/stats/most-yellow-cards-team-statsdetail/2020-21"
t=read_html(url2) %>%
html_nodes("table") %>%
html_table() 

team=data.frame(t)
teamyellow=head(team,10)
datatable(teamyellow)

```


Column {.tabset .tabset-fade data-width=600}
-----------------------------------------------------------------------

### games played vs yellowcards

```{r}

plot(yellowcards$Games.Played,yellowcards$yellow.card,type="p",xlab ="
     games played", ylab ="yellow cards",main="GAMES PLAYED VS YELLOWCARDS CONCEDED",col=rainbow(10),pch=19)
legend("topleft",legend = yellowcards$Player.Name,col = rainbow(10),cex=0.5,fill = rainbow((10)))

```

### player ranking VS per game yellow card average
```{r}

plot(yellowcards$average,yellowcards$Rank,type="p",xlab ="
     yellow card average per game", ylab ="ranking",main="PLAYER RANKING VS PER GAME YELLOWCARD AVERAGE",col=rainbow(10),pch=19)
legend("bottomleft",legend = yellowcards$Player.Name,col = rainbow(10),cex=0.5,fill = rainbow((10)))

```

### barplot for top 10 players with most yellow
```{r}

barplot(yellowcards$yellow.card, width = 0.4,main ="TOP 10 PLAYERS WITH MOST YELLOW CARDS",col = rainbow(10),xlab="yellow card numbers")
legend("topright",legend = yellowcards$Player.Name,col = rainbow(10),cex=0.4,fill = rainbow((10)))
```

### pieplot for YELLOWS CARDS 20/21(clubs)
```{r}

slices=teamyellow$yellow.card
names=teamyellow$Club.Name
pct=round(slices/sum(slices)*100)
new=paste(pct,"%",sep="")
pie(slices,labels = new,main = "YELLOW CARDS 20/21(clubs)",col=rainbow(10))
legend("topleft",legend=teamyellow$Club.Name,col=rainbow(10),cex = 0.4,fill=rainbow(10))

```

# Red Card
Column {data-width=450}
-----------------------------------------------------------------------


### player yellow cards 

```{r}
library(DT)
library(tidyverse)
library(dplyr)
library(rvest)

#DATA FOR PLAYER RED

url3<-"https://sports.ndtv.com/english-premier-league/stats/most-red-cards-player-statsdetail/2020-21"
r=read_html(url3) %>%
  html_nodes("table") %>%
  html_table() 
red=data.frame(r)

redcards=head(red,10)
redcards["average"]=(redcards$red.card/redcards$Games.Played)
datatable(redcards)
```

### TEAM RED CARDS

```{r}
library(DT)
library(tidyverse)
library(dplyr)
library(rvest)

url4<-"https://sports.ndtv.com/english-premier-league/stats/most-red-cards-team-statsdetail/2020-21"
tr=read_html(url4) %>%
  html_nodes("table") %>%
  html_table() 
teamred=data.frame(tr)
teamredcards=head(teamred,10)
datatable(teamredcards)

```


Column {.tabset .tabset-fade data-width=600}
-----------------------------------------------------------------------

### games played vs RED cards

```{r}

plot(redcards$Games.Played,redcards$red.card,type="p",xlab ="
     games played", ylab ="red cards",main="GAMES PLAYED VS RED CARDS CONCEDED",col=rainbow(10),pch=19)
legend("topleft",legend = redcards$Player.Name,col = rainbow(10),cex=0.8,fill = rainbow((10)))

```

### player ranking per game red card average
```{R}
plot(redcards$average,redcards$Rank,type="p",xlab ="
     red card average per game", ylab ="ranking",main="PLAYER RANKING VS PER GAME REDCARD AVERAGE",col=rainbow(10),pch=19)
legend("center",legend = redcards$Player.Name,col = rainbow(10),cex=0.5,fill = rainbow((10)))
```

### correlation between games played vs per game red card average
```{r}

#CORRELATION
# Data generation
set.seed(1)
x <- redcards$average
y <- redcards$Games.Played

# Creating the plot
plot(x, y,xlab = "Passes",ylab = "Wins",main = "RELATIONSHIP BETWEEN PER GAME RED CARD AVERAGE AND GAMES PLAYED", pch = 19, col = rainbow(10))

# Regression line
abline(lm(y ~ x), col = "red", lwd = 3)

# Pearson correlation
text(paste("Correlation:", round(cor(x, y), 2)), x = 17000, y = 25)
cd=cor(x,y)


```

### pie plot
```{r}
slices=teamredcards$red.card
names=teamredcards$Club.Name
pct=round(slices/sum(slices)*100)
new=paste(names,"-",pct,"%",sep="")
pie(slices,labels = new,main = "RED CARDS 20/21(club)",col=rainbow(11:20))
```
